Hector Permafrost

### 2019-09-13 analysis/paper/paper.Rmd
Bugfix sensitivity analysis, and save as PNG

```{r fig-global-sensitivity, fig.cap = global_sensitivity_cap, fig.dim = c(5, 5)}
global_sensitivity_cap <- paste(
  htmlfig(),
  "Sensitivity and variance decomposition analysis for global Hector."
)
readd(sensitivity_plot_sensitivity_global_params_lastyear_global_sims)
```

@@

```{r fig-biome-scatter, fig.cap = biome_scatter_cap, fig.dim = c(8, 8)}
biome_scatter_cap <- paste(
  htmlfig(),
  "Hector outputs (with permafrost biome) at 2100 as a function of input parameter values."
)
fig("biome-scatter.png")
```

@@

```{r fig-biome-sensitivity, fig.cap = biome_sensitivity_cap, fig.dim = c(5, 7)}
biome_sensitivity_cap <- paste(
  htmlfig(),
  "Sensitivity and variance decomposition analysis for Hector with permafrost biome."
)
readd(sensitivity_plot_sensitivity_biome_params_lastyear_biome_sims)
```

>>>>

```{r fig-global-sensitivity, fig.cap = global_sensitivity_cap, fig.dim = c(5, 5)}
global_sensitivity_cap <- paste(
  htmlfig(),
  "Sensitivity and variance decomposition analysis for global Hector."
)
fig("sensitivity-global.png")
```

@@

```{r fig-biome-scatter, fig.cap = biome_scatter_cap}
biome_scatter_cap <- paste(
  htmlfig(),
  "Hector outputs (with permafrost biome) at 2100 as a function of input parameter values."
)
fig("biome-scatter.png")
```

@@

```{r fig-biome-sensitivity, fig.cap = biome_sensitivity_cap}
biome_sensitivity_cap <- paste(
  htmlfig(),
  "Sensitivity and variance decomposition analysis for Hector with permafrost biome."
)
fig("sensitivity-biome.png")
```
